Figures

### 2019-06-17 figures/09_stream_buffer.Rmd
nudge labels

```{r 09_stream_buffer, echo=FALSE, fig.height=3, fig.width=4}
dt <- readRDS("../data/dt.rds") %>%
  dplyr::filter(stream_ag > 0) %>%
  mutate(diff = stream_ag - ag, 
         category = cut(diff, breaks = c(Inf, 28, -28, -Inf))) %>%
  drop_na(diff) %>%
  dplyr::select(lagoslakeid, ag, stream_ag, 
                diff, category, iws_ha) %>%
  arrange(diff)

@@

ggplot(data = dt) +
  geom_point(aes(x = ag, y = stream_ag, color = category)) +
  geom_abline(aes(slope = 1, intercept = 28)) +
  # geom_abline(aes(slope = 1, intercept = 0)) +
  geom_abline(aes(slope = 1, intercept = -28)) +
  ggrepel::geom_text_repel(data = dplyr::filter(dt, lagoslakeid %in% llids), 
            aes(x = ag, y = stream_ag, label = lagoslakeid), nudge_y = 2) + 
  theme_cowplot() +
  theme(legend.position = 0) +
  ylab("Stream buffer Ag (%)") + xlab("IWS Ag (%)") +
  ylim(c(1, 100)) # + xlim(c(40, 100))

>>>>

```{r 09_stream_buffer, echo=FALSE, fig.height=3, fig.width=4}
dt <- readRDS("../data/dt.rds") %>%
  dplyr::filter(stream_ag > 0) %>%
  mutate(diff = stream_ag - ag, 
         category = cut(diff, breaks = c(Inf, 25, -25, -Inf))) %>%
  drop_na(diff) %>%
  dplyr::select(lagoslakeid, ag, stream_ag, 
                diff, category, iws_ha) %>%
  arrange(diff)

@@

ggplot(data = dt) +
  geom_point(aes(x = ag, y = stream_ag, color = category)) +
  geom_abline(aes(slope = 1, intercept = 25)) +
  # geom_abline(aes(slope = 1, intercept = 0)) +
  geom_abline(aes(slope = 1, intercept = -25)) +
  ggrepel::geom_text_repel(data = dplyr::filter(dt, lagoslakeid %in% llids), 
            aes(x = ag, y = stream_ag, label = lagoslakeid), nudge_y = 8) + 
  theme_cowplot() +
  theme(legend.position = 0) +
  ylab("Stream buffer Ag (%)") + xlab("IWS Ag (%)") +
  ylim(c(1, 100)) # + xlim(c(40, 100))
